---
title: "Demonstrate build and calculation of HIO models"
date: "2023-12-02"
output: 
  md_document:
      variant: gfm
---

# Overview

This notebook demonstrates code for building, validating, inspecting, and calculating the HIO models. We proceed one-by-one with the models.

Load useeior
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(useeior) #must be useeior >= 1.4 with hybrid capabilities
```


# USEEIO-WARM

We start with the WARM Integrated Hybrid Model (USEEIO-WARM) with Food and Concrete waste management processes. First build and validate the model. We define the paths to model and related specification files.

```{r}
modelname <- "USEEIO-WARM"
configpaths <- file.path(c("useeior/modelspecs/USEEIO-WARM.yml", "useeior/hybridizationspecs/WARMv15.yml"))
IH <- buildModel(modelname, configpaths)
printValidationResults(IH)
```

Look at the new waste treatment commodities, which are the only model commodities with kg as the unit.
```{r}
df <- IH$Commodities
df <- df[df$Unit=="kg",c("Code","Name")]
knitr::kable(df, row.names = FALSE)

```
See what indicators are available in the model to calculate results 
```{r}
IH$Indicators$meta[,c("Name","Code","Unit")]
```

Calculate a result from the model based on demand of waste treatment.
Use 1000 kg for food waste landfilling.
First create demand vector, calculate the model, and print the LCIA final result

```{r}
y <- setNames(1000, "5622121F/US")
y <- useeior:::formatDemandVector(y, IH$L)
results <- calculateEEIOModel(IH, perspective = "FINAL", y)
lcia <- results[["LCIA_f"]]
lcia["5622121F/US",]
```
The interpretation of the result is the impact of landfilling 1000 tons of food waste in the U.S.
The unit is the units of the model indicator, MTCO2e. 

See the total of the flows for this result (the life cycle inventory results)
```{r}
lci <- results[["LCI_f"]]
print(lci["5622121F/US",])
```


# USEEIO-Waste-Disagg
```{r}
modelname <- "USEEIO-Waste-Disagg"
configpaths <- file.path(c("useeior/modelspecs/USEEIO-Waste-Disagg.yml",
                           "useeior/disaggspecs/LandfillingDisaggregation.yml",
                           "useeior/disaggspecs/562OTHDisaggregation.yml",
                           "useeior/disaggspecs/WasteCombustorsDisaggregation.yml",
                           "useeior/disaggspecs/MRFsDisaggregation.yml"))


WsD <- buildModel(modelname, configpaths)
printValidationResults(WsD)
```


# USEEIO-WIO-Disagg
```{r}
modelname <- "USEEIO-WIO-Disagg"
configpaths <- file.path(c("useeior/modelspecs/USEEIO-WIO-Disagg.yml",
                           "useeior/WIOspecs/DisaggWIOConcrete.yml",
                           "useeior/WIOspecs/DisaggWIOFoodWaste.yml",
                           "useeior/disaggspecs/LandfillingDisaggregation.yml",
                           "useeior/disaggspecs/562OTHDisaggregation.yml",
                           "useeior/disaggspecs/WasteCombustorsDisaggregation.yml",
                           "useeior/disaggspecs/MRFsDisaggregation.yml"))
WD <- buildModel(modelname, configpaths)
printValidationResults(WD)
```



